---
title: "Evaluation of GBMT"
output: html_document
date: "2024-03-18"
---

```{r}
library(tidyverse)
source("R/process_gbmt.R")
#source("R/cluster_stability.R")
```

### Load Data

```{r}
day5 <- read.csv("/projects/b1196/project_5/data/processed/04_5day_intub.csv")
```

### Load in data

We will load in the ten models and rename them all 

```{r}
for(i in list.files("results/Models_logRatio_100_restarts", pattern = ".rda", full.names = TRUE)) {
  
  model_num <- regmatches(i, regexpr("Model_\\d{1,2}", i))
  
  temp <- load(i) %>% get() 
  
  assign(paste(model_num), temp)
  
}

# remove unneeded objects
rm(model_list)
rm(temp)
rm(model_num)
```

```{r}
# create a list of all models
model_list <- list("Model_1" = Model_1, 
                   "Model_2" = Model_2, 
                   "Model_3" = Model_3, 
                   "Model_4" = Model_4, 
                   "Model_5" = Model_5, 
                   "Model_6" = Model_6, 
                   "Model_7" = Model_7,
                   "Model_8" = Model_8,
                   "Model_9" = Model_9, 
                   "Model_10" = Model_10)

## assign group numbers to the sublists
model_list <- rename_gbmt_results(model_list)
```

### Evaluate model statistics across the 10 runs of the model

For each group number between 2-8, we will identify the model with the maximum likelihood and minimum BIC.

```{r}
model_stats <- get_gbmt_stats(model_list)

# identify lowest bic per group number across each of the 10x runs
min_bic_group <- model_stats %>% 
  group_by(group_number) %>% 
  filter(logLik == max(logLik))


# identify maximum liklihood per group number across each of the 10x runs
max_ll_group <- model_stats %>% 
  group_by(group_number) %>% 
  filter(logLik == max(logLik))

# check if dataframe is identical
identical(min_bic_group, max_ll_group)
```
  
  
### Average posterior probability of assginment  
  
```{r}
appa_results <- calc_appa(model_list) 
```

### SD-GMP (Standard dev of assignment probability per group, based on the indiviudals assigned to that group)


```{r}
sdGmp_results <- calc_sdGmp(model_list) %>% 
  mutate(round_result = round(sdGmp, 4))
```

## Proportion of PRF per group

```{r}
assignments <- assign_group(day5, model_list)

props <- assignments %>% 
  # first sum total patients in each group
  group_by(model_number, groups_tested, Group) %>% 
  mutate(count_n_group = n_distinct(anonymized_id)) %>% 
  # group by outcome variable
  group_by(model_number, groups_tested, Group, is_prolonged_14days) %>% 
  # calculate total number of patients by group with each outcome
  mutate(count_pts = n_distinct(anonymized_id)) %>% 
  distinct(model_number, groups_tested, Group, is_prolonged_14days, count_pts, count_n_group) %>% 
  # calculate proportion of patients per group with each outcome
  mutate(prop_outcome = count_pts / count_n_group)
```



**need to review occ**

```{r}
occ_best_model_2 <- calc_occ(Model_3[[1]]); occ_best_model_2
occ_best_model_3 <- calc_occ(Model_2[[2]]); occ_best_model_3
```

**Mismatch**

**outcome assessment**

**cluster stability**

**plots**